Secure Composition \\ of Robust and Optimising Compilers

### 2023-10-11 esop/main.tex
nit

  \item The key contributions of this paper are formalised in the Coq proof assistant and the paper indicates this with \CoqSymbol.
\end{itemize}

This paper starts by introducing relevant notions of security properties and secure compilation (\Cref{sec:background}),
and discusses related work (\Cref{sec:relwork}) before concluding (\Cref{sec:concl}).

@@

\begin{definition}[\glsfirst*{tms}]\label{def:trace:tmsdef}
  \footnotesize$$
  \tmssafe:=\left\{\trace \left| \begin{array}{rcl}
                              \ev{Alloc\ \loc\ n;\sandboxtag;\securitytag}&\le_{\trace}&\ev{Dealloc\ \loc;\sandboxtag;\securitytag'} \\
                              \ev{Use\ \loc\ n;\sandboxtag;\securitytag}&\le_{\trace}&\ev{Dealloc\ \loc;\sandboxtag;\securitytag'} \\
                              \text{if }\ev{Alloc\ \loc\ n;\sandboxtag;\securitytag}\text{ in }\trace&\text{then}&\ev{Dealloc\ \loc;\sandboxtag;\securitytag'}\text{ in }\trace \\
                              \text{at most one }\ev{Dealloc\ \loc;\sandboxtag;\securitytag}&\text{in}&\trace \\
                              \text{at most one }\ev{Alloc\ \loc\ n;\sandboxtag;\securitytag}&\text{in}&\trace \\
                            \end{array}\right.\right\}
  $$
\end{definition}
Hereby, the notation $\event[_{1}]\le_{\trace}\event[_{2}]$ means that if $\event[_{1}]$ is in $\trace$ and if $\event[_{2}]$ is in $\trace$, then $\event[_{1}]$ appears before $\event[_{2}]$.

@@

\begin{center}\small
  \judgbox{\monitorcheck[]{\tmsmonitor}{\tmsmonitor[']}{\absevent}}{,,Monitor $\tmsmonitor$ steps to $\tmsmonitor[']$ given event $\absevent$.''}$\;$\\
  %
% \typerule{tms-uninteresting}{
% }{
%   \monitorcheck[]{\tmsmonitor}{\tmsmonitor}{\absev{\emptyevent}}
% }{tms-uninteresting}
% %
% \typerule{tms-abort}{
% }{
%   \monitorcheck[]{\tmsmonitor}{\tmsmonitor}{\absterm}
% }{tms-abort}
  % 
  \typerule{tms-use}{
    (\loc;\sandboxtag)\in\tmsmonitor.\text{A} 
    &
    % \\
    (\loc;\sandboxtag)\notin\tmsmonitor.\text{F}
  }{
    \monitorcheck[]{\tmsmonitor}{\tmsmonitor}{\absev{Use\ }\loc\ \sandboxtag}
  }{tms-use}
  %
  \typerule{tms-alloc}{
    (\loc;\sandboxtag)\notin\tmsmonitor.\text{A} &
    (\loc;\sandboxtag)\notin\tmsmonitor.\text{F} 
    % \\
    &
    \tmsmonitor[']=\left\{\text{A}: \tmsmonitor.\text{A}\cup\left\{(\loc;\sandboxtag)\right\},\text{F}: \tmsmonitor.\text{F}\right\}
  }{
    \monitorcheck[]{\tmsmonitor}{\tmsmonitor[']}{\absev{Alloc\ }\loc\ \sandboxtag}
  }{tms-alloc}
  %
  \typerule{tms-dealloc}{
    (\loc;\sandboxtag)\in\tmsmonitor.\text{A} 
    &
    (\loc;\sandboxtag)\notin\tmsmonitor.\text{F} 
    \\
    \tmsmonitor[']=\left\{\text{A}: \tmsmonitor.\text{A}\setminus\left\{(\loc;\sandboxtag)\right\} \text{F}: \tmsmonitor.\text{F}\cup\left\{(\loc;\sandboxtag)\right\}\right\}
  }{
    \monitorcheck[]{\tmsmonitor}{\tmsmonitor[']}{\absev{Dealloc\ }\loc\ \sandboxtag}
  }{tms-dealloc}
  %
\end{center}

\Cref{tr:tms-use} simply requires that a location is (i) allocated and (ii) not freed.
\Cref{tr:tms-alloc,tr:tms-dealloc} both require a location to not be freed already and extend the monitor state accordingly.
This restriction effectively disallows reallocation to reassign the same location to an object.
However, the definition can easily be adapted by, e.g., attaching a natural number serving as a counter.
Contrary to other monitors in this paper, the multi-step relation of the \gls*{tms} monitor is non-standard:
\begin{center}
  \judgbox{\monitorcheck{\tmsmonitor}{\tmsmonitor[']}{\abstrace}}{,,Monitor $\tmsmonitor$ multi-steps to $\tmsmonitor[']$ given trace $\abstrace$.''}$\;$\\
  %
  \typerule{tms-refl}{
    \tmsmonitor.\text{allocated}=\emptyset
  }{
    \monitorcheck{\tmsmonitor}{\tmsmonitor}{\hole{\cdot}}
  }{tms-refl}
  %
  \typerule{tms-ign-trans}{
    \monitorcheck{\tmsmonitor}{\tmsmonitor[']}{\abstrace}
  }{
    \monitorcheck[]{\tmsmonitor}{\tmsmonitor[']}{\absev{\emptyevent}\cdot\abstrace}
  }{tms-ign-trans}
  %
  \typerule{tms-trans}{
    \monitorcheck[]{\tmsmonitor}{\tmsmonitor[']}{\absevent} &
    \monitorcheck{\tmsmonitor[']}{\tmsmonitor['']}{\abstrace}
  }{
    \monitorcheck[]{\tmsmonitor}{\tmsmonitor['']}{\absevent\cdot\abstrace}
  }{tms-trans}
\end{center}
\Cref{tr:tms-ign-trans,tr:tms-trans} are the same for all monitors, but \Cref{tr:tms-refl} has, in this case, an additional premise that all locations should be deallocated.
This rejects the behavior of programs that forget to free memory.

@@

\subsubsection{Monitor for \glsfirst*{scct}}
\begin{gather*}
% \small
  \begin{aligned}
    \mi{(Abstract\ Store)}~\scctmonitor:=&\ \emptyset 
    % &
    &
    \mi{(Abstract\ Events)}~\absevent:=&\ \absev{\varepsilon} \mid \absterm \mid \absev{Leak} 
    % \\
  \end{aligned}
\end{gather*}
\begin{center}
  \judgbox{\monitorcheck[]{\scctmonitor}{\scctmonitor[']}{\absevent}}{,,Monitor $\scctmonitor$ steps to $\scctmonitor[']$\\given event $\absevent$.''}$\;$\\
  %
  \typerule{scct-none}{
  }{
    \monitorcheck[]{\scctmonitor}{\scctmonitor}{\absev{\emptyevent}}
  }{scct-none}
  %
  \typerule{scct-abort}{
  }{
    \monitorcheck[]{\scctmonitor}{\scctmonitor}{\absterm}
  }{scct-abort}
\end{center}
The monitor state for the \gls*{scct} monitor is completely empty, since it does not need to keep track of information.
As soon as any event is hit, the execution gets stuck, since any event is considered confidental from the perspective of this monitor.
\begin{center}
  \judgbox{\sccttraceagree[]{\event}{\absevent}}{,,Abstract event $\absevent$ is equivalent to $\event$ w.r.t. \gls*{cct}.''}$\;$\\
  %
  \typerule{scct-low-authentic}{
  }{
    \sccttraceagree[]{\event[_b];\sandboxtag;\unlock}{\absev{\emptyevent}}
  }{scct-low-authentic}
  %
  \typerule{scct-high-authentic}{
  }{
    \sccttraceagree[]{\event[_b];\sandboxtag;\lock}{\absev{Leak}}
  }{scct-high-authentic}
  %
  % \typerule{scct-empty-authentic}{
  % }{
  %   \sccttraceagree[]{\emptyevent}{\absev{\emptyevent}}
  % }{scct-empty-authentic}
  % %
  % \typerule{scct-abort-authentic}{
  % }{
  %   \sccttraceagree[]{\lightning}{\absterm}
  % }{scct-abort-authentic}
\end{center}
Accordingly, the event agreement simply disregards all events that involved public data ($\unlock$) while mapping any other event that does involve private data ($\lock$) to the abstract $\absev{Leak}$ event.

@@

Consider the compilation chain for $\src{TypeScript}$.
First, $\src{TypeScript}$ programs are translated to $\trg{JavaScript}$ which, e.g., V8~\cite{googlev8} eventually compiles in parts to $\irl{Ignition BC}$.
The following theorem establishes what happens if all these compilation steps were robustly secure with respect to \gls*{ms}:
The resulting $\irl{Ignition BC}$ code would be \gls*{ms} regardless of the context the binary runs in.

@@

So far, this paper assumes a unified trace-model between source and target languages.
Moreover secure compilers (in the sense of \Cref{def:rtp}) cannot change the behavior of compiled programs.
It is worth noting that, as our case study in \Cref{sec:casestud:defs} demonstrates, several compilation passes do not change the behavior of compiled programs.
% in such a way that the projections to the specification trace model become unequal to each other, 
% i.e., source and target language of the compiler essentially have a different trace model. 
However, there are instances of passes where this is not the case.
For example, consider $\rtp{\cc{\src{L}}{\trg{L}}}{\tmssafe}$ and $\rtp{\cc{\trg{L}}{\obj{L}}}{\smssafe}$, where $\cc{\trg{L}}{\obj{L}}$ introduces code that allocates a table that stores bounds information of pointers, but fails to insert code that deallocates this table.
By \Thmref{def:trace:tmsdef}, this violates $\tmssafe$.
Therefore, no behavior resulting from programs produced by the $\cc{\trg{L}}{\obj{L}}$ compiler is secure with respect to $\tmssafe$, but only for $\smssafe$.
$\cc{\trg{L}}{\obj{L}}$ modifies the behavior and this section re-introduces the compositionality framework with support for these situations.

@@

The reason we need assumptions about both relations is motivated by \Cref{lem:useless}.
% 
In fact, if \bul{that a relation $\sim_1$ is well-formed for a property $\class$} but \rul{another relation $\sim_2$ is not well-formed for the property mapped with the first relation $\tilde{\tau}_{\sim_1}\class$} then \iul{their composition is empty}.
% 
An empty intersection means that there is no correct behaviour to preserve for the compiler, which nullifies its security relevance.
\begin{lemma}[Composition is Useless]\label{lem:useless}
  If \bul{$\wf{\sim_1}{\class}$}, \rul{$\neg\left(\wf{\sim_2}{\tilde{\tau}_{\sim_1}\class}\right)$}, then \iul{$\tilde{\tau}_{\sim_1\bullet\sim_2}\left(\class\right)=\emptyset$}. \Coqed
\end{lemma}

@@

All presented programming languages share a common fragment. 
Programs ($\prog{\library_{\ctx}}{\library_{\comp}}$) consist of libraries ($\library$), which are lists of functions ($\function$).
Functions ($\lfunction{\textit{foo}}{x}{\expr}$) have a single argument $x$ and an expression ($\expr$) as a body which may have $x$ as a free variable.
Expressions can be variables ($x$), values ($\valueexpr$), binary operations ($\lbinop{\expr[_1]}{\expr[_2]}$), reading from ($\lget{x}{\expr}$) and writing to ($\lset{x}{\expr[_1]}{\expr[_2]}$) memory, memory allocation ($\llet{x}{\lnew{\expr[_1]}{\expr[_2]}}{\expr[_3]}$) as well as deallocation ($\ldelete{x}$), let expressions ($\llet{x}{\expr[_1]}{\expr[_2]}$), pairs ($\lpair{\expr[_1]}{\expr[_2]}$), their first ($\lproja{\expr}$) and second projection ($\lprojb{\expr}$), conditionals ($\lifz{\expr[_1]}{\expr[_2]}{\expr[_3]}$), function calls ($\lcall{\texttt{foo}}{\expr}$), returns ($\lreturn{\expr}$), and an aborting expression ($\labort$).

@@

$\Ltrg$ extends the syntax presented earlier (\Cref{subsec:cs:defs}) with dynamic typechecks ($\trg{\lhast{\expr}{\type}}$) and a way to inspect poison tags ($\trg{\lispoisoned{x}}$) in the metadata of pointers.
For valid pointers ($\trg{\poisonless}$) bound to variable $\trg{x}$, the check $\trg{\lispoisoned{x}}$ yields $\trg{1}$.
If the array bound to $\trg{x}$ was deallocated, i.e., has been poisoned ($\trg{\poisoned}$), the check $\trg{\lispoisoned{x}}$ evaluates to $\trg{0}$.
Dynamic typechecks $\trg{\lhast{\expr}{\type}}$ match on $\trg{\expr}$ and evaluate to $\trg{0}$ if the term is of type $\trg{\type}$ and $\trg{1}$ otherwise.
The projection $\msfilterL{\trg{\trace}}$ is equal to $\msfilterLtms{\src{\trace}}$.

@@

\begin{gather*}\small
  \begin{aligned}
    \cca(\src{x}) = &\ \trg{x} 
    % \\
  	&
    \cca(\src{\lbinop{\expr[_{1}]}{\expr[_{2}]}}) = &\ \lbinop[\trg]{\left[\cca(\src{\expr[_{1}]})\right]}{\left[\cca(\src{\expr[_{2}]})\right]} \\
    \cca(\src{n}) = &\ \trg{n} 
    % \\
    &
    \cca(\src{\lget{x}{\expr}}) = &\ \lget[\trg]{\trg{x}}{\left[\cca(\src{\expr})\right]}
  \end{aligned}
    \\
  \begin{aligned}
    \cca(\src{\ldelete{x}}) = &\ \ldelete[\trg]{\left[\cca(\src{x})\right]} \\
%    \cca(\src{\lset{x}{\expr[_{1}]}{\expr[_{2}]}}) & = \lset[\trg]{\left[\cca(\src{x})\right]}{\left[\cca(\src{\expr[_{1}]})\right]}{\left[\cca(\src{\expr_{2}})\right]} \\
\cca(\src{\lfunction{g}{x:\natt\to\type[_{e}]}{\expr}})  = &\ \lfunction[\trg]{\trg{g}}{\trg{x}}{\lifz[\trg]{\trg{\lhast{x}{\natt}}}{\\%
                                                            &\left[\cca(\src{\expr})\right] %
                                                                                                 }{\labort[\trg]}}
  \end{aligned}
\end{gather*}

@@

\vspace{-1em}
\begin{center}\small
  $$
  \begin{array}{rcl}
    \ccb(\trg{\lnew{x}{\expr[_{1}]}{\expr[_{2}]}}) & = 
    	& \llet[\irl]{\irl{x_{SIZE}}}{\ccb(\trg{\expr[_{1}]})}{
    		% \\&&
    		\lnew[\irl]{\irl{x}}{\irl{x_{SIZE}}}{\ccb(\trg{\expr[_{2}]})}
    		} \\
  \ccb(\trg{\lget{x}{\expr}}) & = 
  	& \llet[\irl]{\irl{x_{n}}}{\ccb(\trg{\expr})}{
  	% \\&&
  	\lifz[\irl]{\irl{0\le x_{n}<x_{SIZE}}}{\irl{\lget{x}{x_{n}}}}{
  		% \\&&
  		\irl{\labort}
  		}
  		} \\
  \ccb(\trg{\lset{x}{\expr[_{1}]}{\expr[_{2}]}}) & = 
  	& \llet[\irl]{\irl{x_{n}}}{\ccb(\trg{\expr[_{1}]})}{
  		\\&&
  		\lifz[\irl]{\irl{0\le x_{n}<x_{SIZE}}}{\lset[\irl]{\irl{x}}{\irl{x_{n}}}{
  		% \\&&
  		\ccb(\trg{\expr[_{2}]})
  		}}{\irl{\labort}}
  		} 
  		% \\
  \end{array}
  $$
\end{center}

>>>>

  \item The key contributions of this paper are formalised in the Coq proof assistant and the paper indicates this with \CoqSymbol.
\end{itemize}
% 
This paper starts by introducing relevant notions of security properties and secure compilation (\Cref{sec:background}),
and discusses related work (\Cref{sec:relwork}) before concluding (\Cref{sec:concl}).

@@

\begin{definition}[\glsfirst*{tms}]\label{def:trace:tmsdef}
  % \footnotesize
  $$
  \tmssafe:=\left\{\trace \left| \begin{array}{rcl}
                              \ev{Alloc\ \loc\ n;\sandboxtag;\securitytag}&\le_{\trace}&\ev{Dealloc\ \loc;\sandboxtag;\securitytag'} \\
                              \ev{Use\ \loc\ n;\sandboxtag;\securitytag}&\le_{\trace}&\ev{Dealloc\ \loc;\sandboxtag;\securitytag'} \\
                              \text{if }\ev{Alloc\ \loc\ n;\sandboxtag;\securitytag}\text{ in }\trace&\text{then}&\ev{Dealloc\ \loc;\sandboxtag;\securitytag'}\text{ in }\trace \\
                              \text{at most one }\ev{Dealloc\ \loc;\sandboxtag;\securitytag}&\text{in}&\trace \\
                              \text{at most one }\ev{Alloc\ \loc\ n;\sandboxtag;\securitytag}&\text{in}&\trace \\
                            \end{array}\right.\right\}
  $$
\end{definition}
Hereby, the notation $\event[_{1}]\le_{\trace}\event[_{2}]$ means that if $\event[_{1}]$ is in $\trace$ and if $\event[_{2}]$ is in $\trace$, then $\event[_{1}]$ appears before $\event[_{2}]$.

@@

\begin{center}\small
  \judgbox{\monitorcheck[]{\tmsmonitor}{\tmsmonitor[']}{\absevent}}{,,Monitor $\tmsmonitor$ steps to $\tmsmonitor[']$ given event $\absevent$.''}$\;$\\
  %
% \typerule{tms-uninteresting}{
% }{
%   \monitorcheck[]{\tmsmonitor}{\tmsmonitor}{\absev{\emptyevent}}
% }{tms-uninteresting}
% %
% \typerule{tms-abort}{
% }{
%   \monitorcheck[]{\tmsmonitor}{\tmsmonitor}{\absterm}
% }{tms-abort}
  % 
  \typerule{tms-use}{
    (\loc;\sandboxtag)\in\tmsmonitor.\text{A} 
    &
    % \\
    (\loc;\sandboxtag)\notin\tmsmonitor.\text{F}
  }{
    \monitorcheck[]{\tmsmonitor}{\tmsmonitor}{\absev{Use\ }\loc\ \sandboxtag}
  }{tms-use}
  %
  \typerule{tms-alloc}{
    (\loc;\sandboxtag)\notin\tmsmonitor.\text{A} &
    (\loc;\sandboxtag)\notin\tmsmonitor.\text{F} 
    % \\
    &
    \tmsmonitor[']=\left\{\text{A}: \tmsmonitor.\text{A}\cup\left\{(\loc;\sandboxtag)\right\},\text{F}: \tmsmonitor.\text{F}\right\}
  }{
    \monitorcheck[]{\tmsmonitor}{\tmsmonitor[']}{\absev{Alloc\ }\loc\ \sandboxtag}
  }{tms-alloc}
  %
  \typerule{tms-dealloc}{
    (\loc;\sandboxtag)\in\tmsmonitor.\text{A} 
    &
    (\loc;\sandboxtag)\notin\tmsmonitor.\text{F} 
    \\
    \tmsmonitor[']=\left\{\text{A}: \tmsmonitor.\text{A}\setminus\left\{(\loc;\sandboxtag)\right\} \text{F}: \tmsmonitor.\text{F}\cup\left\{(\loc;\sandboxtag)\right\}\right\}
  }{
    \monitorcheck[]{\tmsmonitor}{\tmsmonitor[']}{\absev{Dealloc\ }\loc\ \sandboxtag}
  }{tms-dealloc}
  %
\end{center}
% 
\Cref{tr:tms-use} simply requires that a location is (i) allocated and (ii) not freed.
\Cref{tr:tms-alloc,tr:tms-dealloc} both require a location to not be freed already and extend the monitor state accordingly.
This restriction effectively disallows reallocation to reassign the same location to an object.
However, the definition can easily be adapted by, e.g., attaching a natural number serving as a counter.
Contrary to other monitors in this paper, the multi-step relation of the \gls*{tms} monitor is non-standard:
\begin{center}
  \judgbox{\monitorcheck{\tmsmonitor}{\tmsmonitor[']}{\abstrace}}{,,Monitor $\tmsmonitor$ multi-steps to $\tmsmonitor[']$ given trace $\abstrace$.''}$\;$\\
  %
  \typerule{tms-refl}{
    \tmsmonitor.\text{allocated}=\emptyset
  }{
    \monitorcheck{\tmsmonitor}{\tmsmonitor}{\hole{\cdot}}
  }{tms-refl}
  %
  \typerule{tms-ign-trans}{
    \monitorcheck{\tmsmonitor}{\tmsmonitor[']}{\abstrace}
  }{
    \monitorcheck[]{\tmsmonitor}{\tmsmonitor[']}{\absev{\emptyevent}\cdot\abstrace}
  }{tms-ign-trans}
  %
  \typerule{tms-trans}{
    \monitorcheck[]{\tmsmonitor}{\tmsmonitor[']}{\absevent} &
    \monitorcheck{\tmsmonitor[']}{\tmsmonitor['']}{\abstrace}
  }{
    \monitorcheck[]{\tmsmonitor}{\tmsmonitor['']}{\absevent\cdot\abstrace}
  }{tms-trans}
\end{center}
\Cref{tr:tms-ign-trans,tr:tms-trans} are the same for all monitors, but \Cref{tr:tms-refl} has, in this case, an additional premise that all locations should be deallocated.
This rejects the behavior of programs that forget to free memory.

@@

\subsubsection{Monitor for \glsfirst*{scct}}
\begin{gather*}
% \small
  \begin{aligned}
    \mi{(Abstract\ Store)}~\scctmonitor:=&\ \emptyset 
    % &
    &
    \qquad\mi{(Abstract\ Events)}~\absevent:=&\ \absev{\varepsilon} \mid \absterm \mid \absev{Leak} 
    % \\
  \end{aligned}
\end{gather*}
\begin{center}
  \judgbox{\monitorcheck[]{\scctmonitor}{\scctmonitor[']}{\absevent}}{,,Monitor $\scctmonitor$ steps to $\scctmonitor[']$\\given event $\absevent$.''}$\;$\\
  %
  \typerule{scct-none}{
  }{
    \monitorcheck[]{\scctmonitor}{\scctmonitor}{\absev{\emptyevent}}
  }{scct-none}
  %
  \typerule{scct-abort}{
  }{
    \monitorcheck[]{\scctmonitor}{\scctmonitor}{\absterm}
  }{scct-abort}
\end{center}
The monitor state for the \gls*{scct} monitor is completely empty, since it does not need to keep track of information.
% As soon as 
If
any event is hit, the execution gets stuck, since any event is considered confidental from the perspective of this monitor.
\begin{center}
  \judgbox{\sccttraceagree[]{\event}{\absevent}}{,,Abstract event $\absevent$ is equivalent to $\event$ w.r.t. \gls*{cct}.''}$\;$\\
  %
  \typerule{scct-low-authentic}{
  }{
    \sccttraceagree[]{\event[_b];\sandboxtag;\unlock}{\absev{\emptyevent}}
  }{scct-low-authentic}
  %
  \typerule{scct-high-authentic}{
  }{
    \sccttraceagree[]{\event[_b];\sandboxtag;\lock}{\absev{Leak}}
  }{scct-high-authentic}
  %
  % \typerule{scct-empty-authentic}{
  % }{
  %   \sccttraceagree[]{\emptyevent}{\absev{\emptyevent}}
  % }{scct-empty-authentic}
  % %
  % \typerule{scct-abort-authentic}{
  % }{
  %   \sccttraceagree[]{\lightning}{\absterm}
  % }{scct-abort-authentic}
\end{center}
Accordingly, the event agreement simply disregards all events that involved public data ($\unlock$) while mapping any other event that does involve private data ($\lock$) to the abstract $\absev{Leak}$ event.

@@

Consider the compilation chain for $\src{TypeScript}$.
First, $\src{TypeScript}$ programs are translated to $\trg{JavaScript}$ which, e.g., V8~\cite{googlev8} eventually compiles in parts to $\irl{Ignition BC}$.
The following theorem establishes what happens if all these compilation steps were robustly secure with respect to e.g., \gls*{ms}:
The resulting $\irl{Ignition BC}$ code would be \gls*{ms} regardless of the context the binary runs in.

@@

So far, this paper assumes a unified trace-model between source and target languages.
Moreover secure compilers (in the sense of \Cref{def:rtp}) cannot change the behavior of compiled programs.
It is worth noting that, as our case study in \Cref{sec:casestud:defs} demonstrates, several compilation passes do not change the behavior of compiled programs.
% in such a way that the projections to the specification trace model become unequal to each other, 
% i.e., source and target language of the compiler essentially have a different trace model. 
However, there are instances of passes where this is not the case.
For example, consider $\rtp{\cc{\src{L}}{\trg{L}}}{\tmssafe}$ and $\rtp{\cc{\trg{L}}{\obj{L}}}{\smssafe}$, where $\cc{\trg{L}}{\obj{L}}$ introduces code that allocates a table that stores bounds information of pointers, but fails to insert code that deallocates this table.
By \Thmref{def:trace:tmsdef}, this violates $\tmssafe$.
Therefore, no behavior resulting from programs produced by the $\cc{\trg{L}}{\obj{L}}$ compiler is secure with respect to $\tmssafe$, but only for $\smssafe$.
$\cc{\trg{L}}{\obj{L}}$ modifies the behavior of compiled code and this section introduces support for these situations in the compositionality framework.

@@

The reason we need assumptions about both relations is motivated by \Cref{lem:useless}.
% 
In fact, if \bul{a relation $\sim_1$ is well-formed for a property $\class$} but \rul{another relation $\sim_2$ is not well-formed for the property mapped with the first relation $\tilde{\tau}_{\sim_1}\class$} then \iul{their composition is empty}.
% 
An empty intersection means that there is no correct behaviour to preserve for the compiler, which nullifies its security relevance.
\begin{lemma}[Composition is Useless]\label{lem:useless}
  If \bul{$\wf{\sim_1}{\class}$}, \rul{$\neg\left(\wf{\sim_2}{\tilde{\tau}_{\sim_1}\class}\right)$}, then \iul{$\tilde{\tau}_{\sim_1\bullet\sim_2}\left(\class\right)=\emptyset$}. \Coqed
\end{lemma}

@@

All presented programming languages share a common fragment. 
Programs ($\prog{\library_{\ctx}}{\library_{\comp}}$) consist of libraries ($\library$) that belong to a context ($\ctx$) or to a component ($\comp$), and that are lists of functions ($\function$).
Functions ($\lfunction{\textit{foo}}{x}{\expr}$) have a single argument $x$ and an expression ($\expr$) as a body which may have $x$ as a free variable.
Expressions can be variables ($x$), values ($\valueexpr$), binary operations ($\lbinop{\expr[_1]}{\expr[_2]}$), reading from ($\lget{x}{\expr}$) and writing to ($\lset{x}{\expr[_1]}{\expr[_2]}$) memory, memory allocation ($\llet{x}{\lnew{\expr[_1]}{\expr[_2]}}{\expr[_3]}$) as well as deallocation ($\ldelete{x}$), let expressions ($\llet{x}{\expr[_1]}{\expr[_2]}$), pairs ($\lpair{\expr[_1]}{\expr[_2]}$), their first ($\lproja{\expr}$) and second projection ($\lprojb{\expr}$), conditionals ($\lifz{\expr[_1]}{\expr[_2]}{\expr[_3]}$), function calls ($\lcall{\texttt{foo}}{\expr}$), returns ($\lreturn{\expr}$), and an aborting expression ($\labort$).

@@

$\Ltrg$ extends the syntax presented earlier (\Cref{subsec:cs:defs}) with dynamic typechecks ($\trg{\lhast{\expr}{\type}}$) and a way to inspect poison tags ($\trg{\lispoisoned{x}}$) in the metadata of pointers.
For valid pointers ($\trg{\poisonless}$) bound to variable $\trg{x}$, the check $\trg{\lispoisoned{x}}$ yields $\trg{1}$.
If the array bound to $\trg{x}$ was deallocated, i.e., has been poisoned ($\trg{\poisoned}$), the check $\trg{\lispoisoned{x}}$ evaluates to $\trg{0}$.
Dynamic typechecks $\trg{\lhast{\expr}{\type}}$ match on $\trg{\expr}$ and evaluate to $\trg{0}$ if the term is of type $\trg{\type}$ and $\trg{1}$ otherwise.
The projection $\msfilterL{\trg{\trace}}$ is equal to $\msfilterLtms{\src{\trace}}$.
\MPin{
	what is poison. do we need the symbol for valid pointers. 
}

@@

\begin{gather*}
% \small
  \begin{aligned}
    \cca(\src{x}) = &\ \trg{x} 
    % \\
  	&
  	\qquad
    \cca(\src{\lbinop{\expr[_{1}]}{\expr[_{2}]}}) = &\ \lbinop[\trg]{\left[\cca(\src{\expr[_{1}]})\right]}{\left[\cca(\src{\expr[_{2}]})\right]} \\
    \cca(\src{n}) = &\ \trg{n} 
    % \\
    &
    \qquad
    \cca(\src{\lget{x}{\expr}}) = &\ \lget[\trg]{\trg{x}}{\left[\cca(\src{\expr})\right]}
  \end{aligned}
    \\
  \begin{aligned}
    \cca(\src{\ldelete{x}}) = &\ \ldelete[\trg]{\left[\cca(\src{x})\right]} \\
%    \cca(\src{\lset{x}{\expr[_{1}]}{\expr[_{2}]}}) & = \lset[\trg]{\left[\cca(\src{x})\right]}{\left[\cca(\src{\expr[_{1}]})\right]}{\left[\cca(\src{\expr_{2}})\right]} \\
\cca(\src{\lfunction{g}{x:\natt\to\type[_{e}]}{\expr}})  = &\ \lfunction[\trg]{\trg{g}}{\trg{x}}{\lifz[\trg]{\trg{\lhast{x}{\natt}}}{
\\%
                                                            &
                                                            \left[\cca(\src{\expr})\right] %
                                                                                                 }{\labort[\trg]}}
  \end{aligned}
\end{gather*}

@@

\vspace{-1em}
\begin{center}
% \small
  $$
  \begin{array}{rcl}
    \ccb(\trg{\lnew{x}{\expr[_{1}]}{\expr[_{2}]}}) & = 
    	& \llet[\irl]{\irl{x_{SIZE}}}{\ccb(\trg{\expr[_{1}]})}{
    		% \\&&
    		\lnew[\irl]{\irl{x}}{\irl{x_{SIZE}}}{\ccb(\trg{\expr[_{2}]})}
    		} \\
  \ccb(\trg{\lget{x}{\expr}}) & = 
  	& \llet[\irl]{\irl{x_{n}}}{\ccb(\trg{\expr})}{
  	% \\&&
  	\lifz[\irl]{\irl{0\le x_{n}<x_{SIZE}}}{\irl{\lget{x}{x_{n}}}}{
  		% \\&&
  		\irl{\labort}
  		}
  		} \\
  \ccb(\trg{\lset{x}{\expr[_{1}]}{\expr[_{2}]}}) & = 
  	& \llet[\irl]{\irl{x_{n}}}{\ccb(\trg{\expr[_{1}]})}{
  		\\&&
  		\lifz[\irl]{\irl{0\le x_{n}<x_{SIZE}}}{\lset[\irl]{\irl{x}}{\irl{x_{n}}}{
  		% \\&&
  		\ccb(\trg{\expr[_{2}]})
  		}}{\irl{\labort}}
  		} 
  		% \\
  \end{array}
  $$
\end{center}
